Adversarial Training of Neural Networks\\ against Systematic Uncertainty

### 2016-08-30 tex/paper.tex
save

Let $\theta_f$ be fixed and $\hat\theta_r = \arg \max_{\theta_r} E(\theta_f,
\theta_r)$. If $r(f(X;\theta_f) ; \hat\theta_r )_l = p(\lambda_l| f(X; \theta_f)) = \frac{1}{|\Lambda|}$
for all $\lambda_l$, then $f$ is a pivotal quantity.

@@

\glnote{proof 1: if r optimal and r(f(x)) = 1/N then f is pivotal. [OK]}
\glnote{proof 2: if Lf can be minimized under the pivotal constraint, then at the saddle point r is such that r(f(x)) = 1/N. [OK]}

>>>>

Let $\theta_f$ be fixed and $\hat\theta_r = \arg \max_{\theta_r} E(\theta_f,
\theta_r)$. If $r(f(X;\theta_f) ; \hat\theta_r )_l = \frac{1}{|\Lambda|}$
for all $\lambda_l$, then $f$ is a pivotal quantity.

@@

\begin{proof}

Let us first recall that the cross-entropy for distributions $p$ and $q$ is
minimized when $p=q$. For ${\cal L}_r$ defined as the cross-entropy between the
true conditional distribution of the nuisance $p_{\lambda|f(X;\theta_f)}$ and
the approximate conditional distribution of the nuisance
$p_{r(f(X;\theta_f);\theta_r)|f(X)}$, the optimal parameters $\hat\theta_r =
\arg \max_{\theta_r} E(\theta_f, \theta_r) = \arg \min_{\theta_r} L_r(\theta_f,
\theta_r)$ are therefore such that $p_{\lambda|f(X;\theta_f)} =
p_{r(f(X;\theta_f);\hat\theta_r)|f(X)}$.

In other words, for all $\lambda_l \in  \Lambda$, we have $r(f(X;\theta_f);\hat\theta_r)_l = p(\lambda_l|f(X;\theta_f))$.
By assumption, $r(f(X;\theta_f);\hat\theta_r)_l = \frac{1}{|\Lambda|}$,
and therefore $p(\lambda_l|f(X;\theta_f)) = \frac{1}{|\Lambda|}$.
Using the Bayes' rule, we write
\begin{align*}
    p(f(X;\theta_f)|\lambda_l) &= \frac{ p(\lambda_l|f(X;\theta_f)) p(f(X;\theta_f)) } { p(\lambda_l)} \\
                               &= \frac{ \tfrac{1}{|\Lambda|} p(f(X;\theta_f)) } { \tfrac{1}{|\Lambda|} } \\
                               &= p(f(X;\theta_f)),
\end{align*}
which holds for all $\lambda_l \in \Lambda$ and implies that $f$ is a pivotal quantity.
\end{proof}

\begin{proposition}
\glnote{proof 2: if Lf can be minimized under the pivotal constraint, then at the saddle point r is such that r(f(x)) = 1/N. [OK]}
\end{proposition}
